Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-29 main-disk-model.tex
minor, equation

    \subsection{Workflow}
    \label{sec.mod.work}
    A workflow is modeled as a directed acyclic graph $G=(V, E)$, where $V$ is the set of vertices (tasks), and
    $E$ is a set of directed edges of the form $e=(u,v)$, with $u,v\in V$, expressing precedence constraints between tasks.
    Each task~$u \in V$  is performing $w_u$ operations, and it also
    requires some amount of memory to be executed, denoted as~$m_u$.
    Each edge $e=(u,v) \in E$ has a cost~$c_{u,v}$ that corresponds to the size of the output file written by task~$u$ and used as input by task~$v$.
   \skug{here?: For each edge, we also keep information on where it is currently stored - in memory of a processor (with processor id),
    on the disk or nowhere - if this file has not yet been generated or has already been consumed by the successor task.}
    Note that $m_u$ is the total memory usage
    of a task during its execution, including input and output files currently being read and written,
    and hence the total memory requirement  for the execution of task~$u$ consists of the maximum
    between the input files
    (total size of the files to be received from the parents),
    the output files (total size of the files to be sent to the children),
    and the total memory size~$m_u$ (usually achieving the maximum):
    \[
        r_u = \max\left\{m_u , \sum_{v:(v,u)\in E}c_{v,u}, \sum_{v:(u,v)\in E} c_{u,v}\right\}.
    \]

@@

    \[
        w_{real} = \frac{w_u}{s_j} \* (1 + (m_i - M_j)/m_i ) \* q_s.
    \]
where $q_s$ sit he slowdown coefficient and $(m_i - M_j)/m_i$ is the part of the task memory that needs to be offloaded.
    \skug{check this equation}
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

>>>>

    \subsection{Workflow}
    \label{sec.mod.work}
    A workflow is modeled as a directed acyclic graph $G=(V, E)$, where $V$ is the set of vertices (tasks), and
    $E$ is a set of directed edges of the form $e=(u,v)$, with $u,v\in V$, expressing precedence constraints between tasks.
    Each task~$u \in V$  is performing $w_u$ operations, and it also
    requires some amount of memory to be executed, denoted as~$m_u$.
    Each edge $e=(u,v) \in E$ has a cost~$c_{u,v}$ that corresponds to the size of the output file written by task~$u$ and used as input by task~$v$.

    Note that $m_u$ is the total memory usage
    of a task during its execution, including input and output files currently being read and written,
    and hence the total memory requirement  for the execution of task~$u$ consists of the maximum
    between the input files
    (total size of the files to be received from the parents),
    the output files (total size of the files to be sent to the children),
    and the total memory size~$m_u$ (usually achieving the maximum):
    \[
        r_u = \max\left\{m_u , \sum_{v:(v,u)\in E}c_{v,u}, \sum_{v:(u,v)\in E} c_{u,v}\right\}.
    \]

@@

    \[
        w_{real} = \frac{w_u}{s_j} +    \frac{q_s \times w_u}{s_j} \frac{m_i - M_j}{m_i}
    \]
where $q_s$ sit he slowdown coefficient and $(m_i - M_j)/m_i$ is the part of the task memory that needs to be offloaded.
    \skug{check this equation}
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

\skug{For each edge, we also keep information on where it is currently stored - in memory of a processor (with processor id),
        on the disk or nowhere - if this file has not yet been generated or has already been consumed by the successor task.}
